The imprint of global magma oceans on exoplanet demographics

### 2023-03-22 src/tex/ms.tex
assess TESS sample size
include new Tamburo+23 yields for Roman transiters

Similarly, the Transiting Exoplanet Survey Satellite~\citep[\tess,][]{Ricker2014a} planet sample lacks temperate, small planets around bright host stars~\citep{Ment2023}, as was expected from planet yield calculations~\citep{Barclay2018}.

@@

While not primarily designed to detect transiting planets, the \rst~\citep{Spergel2015} is expected to yield $\sim 10^5$ transiting planets on short orbits and constrain their radii in the course of its mission~\citep{Montet2017}.
In a fraction of the cases, planets as small as \SI{2}{\Rearth} will be detected.
About 200 planets smaller than Neptune are expected to be found around M~dwarfs and thus may reach into the habitable zone.
The \rst\ could thus provide a useful sample to explore the runaway greenhouse transition, albeit with a predominant focus on water-rich (sub-)Neptunes~\citep[e.g.,][]{Pierrehumbert2022}.

>>>>

Similarly, the Transiting Exoplanet Survey Satellite~\citep[\tess,][]{Ricker2014a} planet sample lacks temperate, small planets around bright host stars~\citep{Ment2023}, as was expected from planet yield calculations~\citep{Barclay2018}.
As of 2023 March 22, the NASA Exoplanet Archive\footnote{\url{https://exoplanetarchive.ipac.caltech.edu}} lists 40 \tess\ candidate or confirmed planets smaller than \SI{4}{\rEarth} with lower estimated instellation than Earth's.

@@

While not primarily designed to detect transiting planets, the Galactic Bulge Time Domain Survey of the \rst~\citep{Spergel2015} is expected to yield $\sim 10^5$ transiting planets on short orbits and constrain their radii in the course of its mission~\citep{Montet2017}.
%In a fraction of the cases, planets as small as \SI{2}{\Rearth} will be detected.
$\mathcal{O} (1000)$ planets smaller than Neptune could be found around early to mid-M~dwarfs, however, only a small fraction of them will reach into the habitable zone~\citep{Tamburo2023}.
We thus conclude that the \rst\ could provide a useful sample to explore the runaway greenhouse transition, albeit with a predominant focus on water-rich (sub-)Neptunes~\citep[e.g.,][]{Pierrehumbert2022}.
